Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-16 doc/PRF2022/PRF_main.tex
edits

%% ***A*** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The JPs are disks of radius $c$ suspended in a viscous solvent
with center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$.
The sets $\Omega$, $\Gamma_1$, \dots, and $\Gamma_{N_b}$ depend on $t$.
Assuming inertial terms are negligible, we have the Stokes equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
\label{eq:stokesMass}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokesFarfield}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
solvent viscosity. The solvent velocity satisfies the no-slip boundary
condition for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

To obtain forces, define the free
energy~\cite{Fu20, Fu2022_JFM}
\begin{align}
\label{eq:free_energy}
F = \gamma
  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right),
\end{align}
where $u(\xx,t)$ is as the order parameter for water\cite{Ma77, GoHaKo94},
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
The order parameter $u(\xx,t)$ is assumed to minimize the free energy
$F$ and therefore satisfies the screened Laplace equation
boundary value problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.
The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
\infty$. The parameter $\rho_0$ is the distance 
below which steric repulsion becomes important and 
$M$ is the repulsion modulus.

Letting $\nnu$ be the particle outward normal,
the force $\FF_i$ and torque $T_i$ coming from the free energy
acting on $\Gamma_i$ are~\cite{Fu20}
%from the
%free energy~\cite{Fu20}, we compute the variation of the domain of the
%free energy~\eqref{eq:free_energy} subject
%to~\eqref{eq:SL}--\eqref{eq:SLbc},
%and obtain 
\begin{align}
  \label{eq:FandTdef}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{align}
Here,
\begin{align}
\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
is the second-order hydrophobic stress tensor.
Repulsion is rotationally symmetric and
does not enter $T_i$.

@@

To perform a single time step, we
(i) solve~\eqref{eq:SL}--\eqref{eq:SLbc} for $u$,
(ii) compute the force and torque~\eqref{eq:FandTdef},
and finally (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
subject to~\eqref{eq:rigid-vel} and \eqref{eq:force}. 
The velocities $(\vv_i, \omega_i)$ obtained
from~\eqref{eq:rigid-vel} are used to update the
particle positions and orientations
using the second-order Adams-Bashforth scheme
with time step size $\Delta t.$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representations}
It is challenging to solve the Stokes and screened Laplace equations
and far-field boundary conditions accurately. 
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\sigma$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \partial \Omega$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
    \xx \in \Gamma.
\end{align}

For the velocity, we use the representation
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
%Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
%unique solution, but we note that
Alternative full-rank layer potential
representations for rigid body motions are possible~\cite{rac-gre2016,
cor-gre-rac-vee2017}.

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $2NN_b \times 2NN_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES, and we guarantee that the
number of GMRES iterations is mesh-independent by using second-kind
BIEs.

@@

\section{Tunable hydrophobicity}
\label{sec:tunable_hydrophobicity}
The parameters are modeled after those for
phospholipid in water~\cite{Boal}.
We use $\mu = 1$~mPa~s for the viscosity of water
at room temperature. Pure lipid components give a range of interfacial
tensions $0.7$--$5.3$~pN~nm$^{-1}$~\cite{KUZMIN2005, Petelska2012,
  Jackson2016, GarciaSaez}.
we use $\gamma=4.1$~pN~nm$^{-1}$ since
this value gave good agreement with elastic moduli of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
The particle radius $c = 1.25$~nm represents one half 
of phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
derives from experimental force-distance measurements of hydrophobic
attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. 
A repulsion modulus $M = 2$~pN and 
distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
particle radius, ensuring the accuracy of the boundary integral
representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without 
overly aggressive mesh refinement. The characteristic time
and length are $1$~ns and  $1$~nm respectively.

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
  and director $\dd$, along with the angle $\alpha$.
  The three rightmost panels plots show $g(\xx)$ and
  the respective solutions $u(\xx)$ of~\eqref{eq:SL} 
  for an isolated particle.}
\end{caption}
\end{figure}
\subsection{Boundary conditions and equilibrium configurations}
The boundary condition $g(\xx)$ in
\eqref{eq:SLbc} defines the spatial distribution of
hydrophobicity and hydrophilicity.
Referring to Figure \ref{fig:boundary_conditions},
\begin{align}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{align}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and the
particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$
The scalar $a$ normalizes $g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
The side of the particle where
$\alpha = 0$ is called the tail and the side where $\alpha = \pi$ is the head.

Based on the choice of $b$,
the boundary condition (BC) \eqref{eq:bc-type}
can be classified into one of three categories:
(Type I, amphiphile, $b = 1$) $g$ is positive on 
one side representing a hydrocarbon-water interface, and
is zero on the other representing an apolar, hydrophilic region;
(Type II, asymmetric hydrophobe, $b = 2$) $g$ is positive
on both sides but greater on one side;
(Type III, poler, $b = -1/2$) $g$ is positive on one
side and negative on the other, representing a
water structure with positive/negative charge~\cite{MaRa76, Ma77}.

@@

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure1and2.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
%  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows the initial $N_b = 198$ particle configuration with random
  position and orientation.
  Panels (b), (d), (e) show bilayer, multilamellar, and striated phases
  composed of amphiphilic (Type I), asymmetric hydrophobic (Type II),
  and poler (Type 3) JP, respectively. 
  Panels (c) and (f) plot the free energies~\eqref{eq:free_energy}
  and alignment order parameter~\eqref{eq:S2} with respect
  to $t$. The solid markers in panel (c) are 
  normalized by $60/198$, showing that the energy
  approximately scales with the number of particles.
  Alignment in the striated phase is particle-number dependent; 
  triangle markers, panel (f).}  
\end{caption}
\end{figure}

For Type II, asymmetric hydrophobes,
both sides of the JP are hydrophobic but more so on the tail.
Over short times, these particles self-assemble into bilayers. But unlike for
Type I JP, the heads are also hydrophobic and so over long times, 
the bilayers sort into a ``multilamellar'' phase.
The number of layers depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
with four layers and one with two layers in the inset.
Onion-like dendrimersomes have previously been studied by molecular dynamics
simulations using an 
anisotropic pair potential~\cite{C9NR05885K,HongCacciutoLuijtenGranick2008}.

@@

Finally, we use the scalar order parameter $S_2$
to quantify the orientational order\cite{Selinger2016}:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta_i$ is a circular mean defined as the orientation of the
principal eigenvector of the matrix
$\sum_{j} \dd_j\dd_j^\top$ where $j$ runs over the particles
whose centers lie with $4c$ of that of particle $i$. 
Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le 1$.
with a value $S_2 = 1$ indicates perfect alignment between particles
while $S_2=-1/2$ indicates isotropic alignment locally.
This cutoff distance was chosen empirically
so that the average includes nearest neighbors
but excludes next nearest neighbors.

@@

The striated phase order admits more than one pattern
depending on the number of particles (Figure~\ref{fig:relax}(f), bottom and top curves).
When the number of particles is fewer, there is only a
single pattern in particle orientations where the directors are more or
less parallel and alternate directions (Figure~\ref{fig:relax}(e),
inset). Larger number of particles results in multiple alignment patterns:
the alternating sign pattern as in the small particle number case
(Figure~\ref{fig:relax}(e), top right rectangle) and an 'X'-shaped
alignment (Figure~\ref{fig:relax}(e), top left rectangle).

>>>>

%% ***** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The JPs are disks of radius $c$ suspended in a viscous solvent
with center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$.
The sets $\Omega$, $\Gamma_1$, \dots, and $\Gamma_{N_b}$ depend on $t$.
Assuming inertial terms are negligible, the solvent satisfies the Stokes equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
\label{eq:stokesMass}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokesFarfield}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
solvent viscosity. The solvent velocity satisfies the no-slip boundary
condition for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

To obtain forces, define the free
energy~\cite{Fu20, Fu2022_JFM}
\begin{align}
\label{eq:free_energy}
F = \gamma
  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right),
\end{align}
where $u(\xx,t)$ is as the order parameter for water\cite{Ma77, GoHaKo94},
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
The order parameter $u(\xx,t)$ is assumed to minimize the free energy
$F$ and therefore satisfies the screened Laplace boundary value problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.
The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for
$s \geq 1$. The parameter $\rho_0$ is the distance 
below which steric repulsion becomes important and 
$M$ is the repulsion modulus.

Letting $\nnu$ be the particle outward normal,
the force $\FF_i$ and torque $T_i$ coming from the free energy
acting on $\Gamma_i$ are~\cite{Fu20}
%from the
%free energy~\cite{Fu20}, we compute the variation of the domain of the
%free energy~\eqref{eq:free_energy} subject
%to~\eqref{eq:SL}--\eqref{eq:SLbc},
%and obtain 
\begin{align}
  \label{eq:FandTdef}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s.
\end{align}
Here,
\begin{align}
\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
is the second-order hydrophobic stress tensor.
Repulsion is rotationally symmetric and
does not enter $T_i$.

@@

To perform a single time step, we
(i) solve~\eqref{eq:SL}--\eqref{eq:SLbc} for $u$,
(ii) compute the force and torque~\eqref{eq:FandTdef},
and (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
subject to~\eqref{eq:rigid-vel} and \eqref{eq:force}. 
The velocities $(\vv_i, \omega_i)$ obtained
from~\eqref{eq:rigid-vel} are used to update the
particle positions and orientations
using the second-order Adams-Bashforth scheme
with time step size $\Delta t.$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representations}
We require a method to accurately solve the Stokes and
screened Laplace equations in intricate, unbounded geometries.
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\eta(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\eta$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \partial \Omega$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \eta(\xx) + \DD[\eta](\xx), \quad
    \xx \in \partial \Omega.
\end{align}

For the velocity, we use the completed double-layer potential
representation~\cite{pow-mir1987}
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
%Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
%unique solution, but we note that
Alternative full-rank layer potential
representations for rigid body motions are possible~\cite{rac-gre2016,
cor-gre-rac-vee2017}.

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $2NN_b \times 2NN_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES
and the second-kind BIEs
guarantee that the number of GMRES iterations is
mesh-independent.

@@

\section{Tunable hydrophobicity}
\label{sec:tunable_hydrophobicity}
The parameters are modeled after those for
phospholipid in water~\cite{Boal}.
We use $\mu = 1$~mPa~s for the viscosity of water
at room temperature. Pure lipid components give a range of interfacial
tensions~\cite{KUZMIN2005, Petelska2012,Jackson2016, GarciaSaez}; $0.7$--$5.3$~pN~nm$^{-1}$.
We use $\gamma=4.1$~pN~nm$^{-1}$ which gives a physically reasonable 
elastic modulus $\kappa$ of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
The particle radius $c = 1.25$~nm represents one half 
of phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
derives from experimental force-distance measurements of hydrophobic
attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. 
A repulsion modulus $M = 2$~pN and 
distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
particle radius, ensuring the accuracy of the boundary integral
representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without 
overly aggressive mesh refinement. The characteristic time
and length are $1$~ns and  $1$~nm, respectively.

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
  and director $\dd$, along with the angle $\alpha$.
  The three rightmost panels plots show $g(\xx)$ and
  the respective solutions $u(\xx)$ of~\eqref{eq:SL} 
  for an isolated particle.}
\end{caption}
\end{figure}
\subsection{Boundary conditions and equilibrium configurations}
The boundary condition $g(\xx)$ in
\eqref{eq:SLbc} defines the spatial distribution of
hydrophobicity and hydrophilicity.
Referring to Figure \ref{fig:boundary_conditions},
\begin{align}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{align}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and the
particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$
The scalar $b$ shifts the periodic date up and down and the scalar
$a$ normalizes $g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
The side of the particle where
$\alpha = 0$ is called the tail and the side where $\alpha = \pi$ is the head.

Based on the choice of $b$,
the boundary condition (BC) \eqref{eq:bc-type}
can be classified into one of three categories:
Type I, amphiphile, $b = 1$, $g$ is positive on 
one side representing a hydrocarbon-water interface, and
is zero on the other representing an apolar, hydrophilic region;
Type II, asymmetric hydrophobe, $b = 2$, $g$ is positive
on both sides but more so on one side;
Type III, polar, $b = 0$, $g$ is positive on one
side and negative on the other, representing a
water structure with positive/negative charge~\cite{MaRa76, Ma77}.

@@

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure1and2.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
%  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
    Panel (a) shows the $t = 0$, $N_b = 198$ particle configuration
    with random orientation and initially confined to a box. 
  Panels (b), (d), (e) show bilayer, multilamellar, and striated phases
  composed of amphiphilic (Type I), asymmetric hydrophobe (Type II),
  and polar (Type III) JP, respectively. 
  Panels (c) and (f) plot the free energies~\eqref{eq:free_energy}
  and alignment order parameter~\eqref{eq:S2} with respect
  to $t$. The open markers in panel (c)
  are for $N_b = 60$ and the
  solid markers are for $N_b = 198$ but 
  normalized by $60/198$, showing that the energy
  approximately scales with the number of particles.
  Alignment in the striated phase is particle-number dependent; 
  triangle markers, panel (f).}  
\end{caption}
\end{figure}

For Type II, asymmetric hydrophobes,
both sides of the JP are hydrophobic but more so on the tail.
Over short times, these particles self-assemble into bilayers. But unlike for
Type I JPs, the heads are also hydrophobic and so over long times, 
the bilayers sort into a ``multilamellar'' phase.
The number of layers depends on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
with four layers and one with two layers in the inset.
Onion-like dendrimersomes have previously been studied by molecular dynamics
simulations using an 
anisotropic pair potential~\cite{C9NR05885K,HongCacciutoLuijtenGranick2008}.

@@

Finally, we use the scalar order parameter $S_2$
to quantify the orientational order\cite{Selinger2016}:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta_i$ is a circular mean defined as the orientation of the
principal eigenvector of the matrix
$\sum_{j} \dd_j\dd_j^\top$ where $j$ runs over the particles
whose centers lie with $4c$ of that of particle $i$. 
Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le 1$
with a value $S_2 = 1$ indicating perfect alignment between particles
while $S_2=-1/2$ indicating isotropic alignment locally.
The cutoff distance $4c$ was chosen empirically
so that the average includes nearest neighbors
but excludes next nearest neighbors.

@@

The striated phase order admits more than one pattern
depending on the number of particles (Figure~\ref{fig:relax}(f), triangles).
When the number of particles is fewer, there is only a
single pattern where the directors are more or
less parallel and alternate directions (Figure~\ref{fig:relax}(e),
inset). Larger number of particles results in multiple alignment patterns:
the alternating sign pattern as in the small particle number case
(Figure~\ref{fig:relax}(e), top right rectangle) and an 'X'-shaped
alignment (Figure~\ref{fig:relax}(e), top left rectangle).
